A Context Menu for the Real World: Controlling Physical Devices Through Head-Worn Infrared Targeting

### 2013-09-16 doc/sigchi14/targeting.tex
added numbers to participants

\subsection{Participants}
We recruited \bjoern{N} participants from our institution. \bjoern{X} had never used Glass before. \bjoern{Y} wore prescription glasses, which may have affected their task performance as wearing both Glass and regular glasses is possible, but leads to \bjoern{explain problems}.

>>>>

\subsection{Participants}
We recruited 15 participants from our institution. 13 had never used Glass before. 4 wore prescription glasses, which may have affected their task performance \claire as the glasses beneath Glass make it more cumbersome to secure the position of the Glass and to adjust the screen to the optimal angle.
